First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-05-16 ms.tex
More touchups to text of paper

The top panel of Figure~\ref{fig:cables} shows a 2D power spectrum using the gain model 
described so far. Three of the horizontal lines in the EoR window can be attributed to the 
coarse band gaps, as they reside at the harmonics expected for 1.28~MHz periodic 
sampling. But the sampling cannot account for the fourth line, highlighted by the arrow. The 
corresponding delay time of the line, $\tau \approx 1.23$~$\mu$s, corresponds almost 
exactly to twice the signal travel time through the 150 meter cables (with velocity 0.81c). We 
therefore introduced a reflection term into our gain model, which allows our restricted gains 
to account for the interference of the incident signal with a round-trip reflected signal in the 
cable. The full gain model is expressed as
\begin{equation}\label{eq:cal2}
\hat{g}_i(\nu)=B_{\alpha}(\nu)\left(P_i(\nu)+R_i(\nu)\right),
\end{equation}
where the reflection term can be further decomposed as
\begin{equation}
R_i(\nu) = R_{i,0} e^{-2\pi i \tau_{i} \nu}.
\end{equation}
The reflection coefficient, $R_{i,0}$ is allowed to be complex, while the reflection delay, 
$\tau_i$ is real. After fitting for all other parameters, we fit for the reflection mode. This is 
done for antennas with suspected reflections, the most offensive of which is seen in the 
antennas with cables of 150 meters. Because the cables were not cut at exact lengths 
(variations on order tens of centimeters), we solve for both the reflection coefficient and 
delay by performing a direct Fourier transform to a highly over resolved delay grid and 
selecting the mode where the reflection amplitude is largest.

@@

\textcolor{red}{this needs to be rewritten}
In all bands and polarizations, we are heavily signal dominated in our most sensitive region 
(low $k$). This is not surprising based on the 2D spectra we examined earlier. We can see 
the strong coarse band harmonic lines, and the cable reflection line between the first two 
coarse band lines. But between these coarse lines there are bins which approach the noise 
level and are consistent with zero (notably the North-South polarization for the $z=7.1$ and 
$z=6.8$ bands). These regions are encouraging because they have the potential to 
continue integrating down with more data.

However, our best upper limits for a cosmological signal are still at low $k$, despite the 
strong leakage. Because any foreground leakage should not correlate with the EoR signal, 
we can assume that the power of the sum of leakage and cosmological signal is greater 
than the power of the EoR signal alone, allowing us to set an upper limit. We quote the best 
2-$\sigma$ upper limits, $\Delta^2_{\text{UL}}$, for each polarization and band in Table~
\ref{tbl:limits}. These limits and their context in the field are further discussed in Section~
\ref{sec:discussion}.

\begin{table}
\begin{center}
\caption[EoR power spectrum limits]{Upper limits on the EoR power spectrum for our three 
sub-bands and two polarizations. Upper limits, $\Delta^2_{\text{UL}}$, are at 97.7\% 
confidence level.
\label{tbl:limits}
}
\begin{tabular}{ccccc}
\tableline\tableline
Sub-band & $z_0$ & Polarization & $k$ (h Mpc$^{-1}$) & $\Delta^2_{\text{UL}}$ (mK$^2$) \\
\tableline
Low & 7.1 & E-W & 0.231 & 3.02 $\times 10^4$\\
Low & 7.1 & N-S & 0.231 & 2.22 $\times 10^4$\\
Mid & 6.8 & E-W & 0.2361 & 2.84 $\times 10^4$\\
Mid & 6.8 & N-S & 0.2361 & 2.17 $\times 10^4$\\
High & 6.5 & E-W & 0.204 & 5.24 $\times 10^4$\\
High & 6.5 & N-S & 0.241 & 3.11 $\times 10^4$\\
\tableline
\end{tabular}
\end{center}
\end{table}

>>>>

The top panel of Figure~\ref{fig:cables} shows a 2D power spectrum using the gain model 
described so far. Three of the horizontal lines in the EoR window can be attributed to the 
coarse band gaps, as they reside at the harmonics expected for 1.28~MHz periodic 
sampling. But the sampling cannot account for the fourth line, highlighted by the arrow. The 
corresponding delay time of the line, $\tau \approx 1.23$~$\mu$s, corresponds almost 
exactly to twice the signal travel time through the 150 meter cables (with velocity 0.81c). We 
therefore introduced a reflection term into our gain model, which allows our restricted gains 
to account for the interference of the incident signal with a round-trip reflected signal in the 
cable. 
A similar approach was taken at lower frequencies in \citealt{Ewall-Wice:2016}.
The full gain model is expressed as
\begin{equation}\label{eq:cal2}
\hat{g}_i(\nu)=B_{\alpha}(\nu)\left(P_i(\nu)+R_i(\nu)\right),
\end{equation}
where the reflection term can be further decomposed as
\begin{equation}
R_i(\nu) = R_{i,0} e^{-2\pi i \tau_{i} \nu}.
\end{equation}
The reflection coefficient, $R_{i,0}$ is allowed to be complex, while the reflection delay, 
$\tau_i$ is real. After fitting for all other parameters, we fit for the reflection mode. This is 
done for antennas with suspected reflections, the most offensive of which is seen in the 
antennas with cables of 150 meters. Because the cables were not cut at exact lengths 
(variations on order tens of centimeters), we solve for both the reflection coefficient and 
delay by performing a direct Fourier transform to a highly over resolved delay grid and 
selecting the mode where the reflection amplitude is largest.

@@

In all bands and polarizations, we are heavily signal dominated in our most sensitive region
(low $k$). This is not surprising based on the 2D spectra we examined earlier. The gaps in
the data are due to the excised coarse band harmonics. We can see the cable reflection line
between the first two gaps in all polarizations and sub-bands. Between the coarse band
harmonic lines, especially at larger $k$, are bins which approach the noise level and are
consistent with zero (notably the North-South polarization for the low and mid bands). The
bin just above the first coarse band harmonic is also consistent with zero in the low band.
These regions are encouraging because they have the potential to continue integrating down
with more data. Improved suppression of the coarse band harmonic and cable reflection lines
will also improve the limits presented here.

Our best upper limits for a cosmological signal are at low $k$, despite the 
strong leakage. Because any foreground leakage should not correlate with the EoR signal, 
we can assume that the power of the sum of leakage and cosmological signal is greater 
than the power of the EoR signal alone, allowing us to set an upper limit. We quote the best 
2-$\sigma$ upper limits, $\Delta^2_{\text{UL}}$, for each polarization and band in Table~
\ref{tbl:limits}. These limits and their context in the field are further discussed in Section~
\ref{sec:discussion}.

\begin{table}
\begin{center}
\caption[EoR power spectrum limits]{Upper limits on the EoR power spectrum for our three 
sub-bands and two polarizations. Upper limits, $\Delta^2_{\text{UL}}$, are at 97.7\% 
confidence level.
\label{tbl:limits}
}
\begin{tabular}{ccccc}
\tableline\tableline
Sub-band & $z_0$ & Polarization & $k$ (h Mpc$^{-1}$) & $\Delta^2_{\text{UL}}$ (mK$^2$) \\
\tableline
Low & 7.1 & E-W & 0.231 & 3.67 $\times 10^4$\\
Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$\\
Mid & 6.8 & E-W & 0.24 & 3.56 $\times 10^4$\\
Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$\\
High & 6.5 & E-W & 0.20 & 4.70 $\times 10^4$\\
High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$\\
\tableline
\end{tabular}
\end{center}
\end{table}
